The proof equivalence problem for multiplicative linear logic is \textsc{pspace}-complete v0.3

### 2014-01-03 main/s_level_2.tex
tinkering with proofs and defs.

A \emph{configuration} of an \textsc{ncg} is a function $\gamma\colon E\to V$ such that
\begin{itemize}
	\item
$\gamma(e)\in v(e)$ for every edge $e$, and
	\item
for every vertex $v$, the sum of its inflow weights $\sum\{w(e)\mid \gamma(e)=v\}$ is equal to or greater than its inflow constraint $c(v)$.
\end{itemize}

A \emph{reconfiguration step} $\gamma\sim\delta$ connects two configurations for a \textsc{ncg} $G$ that differ in the assignment $\gamma(e)$ of exactly one edge.

@@

%\begin{lemma}
%If the permutation $\links\sim\links'$ consists of the re-attachment of exactly one jump, then $\coitn\links$ and $\coitn{\links'}$ differ on the value of at most one edge.
%\end{lemma}

% THIS IS FALSE : OTHER EDGES MAY BE CONNECTED *VIA* THE ONE THAT IS MOVED

By the above, a proof net for $\itn G$ gives a partial function from edges to vertices.

\begin{definition}
	For a proof net $\links$ for the interpretation of a graph $\itn G$, let $\coitn\links\colon E\rightharpoonup V$ be the partial function where $\coitn\links(e)$ is $v$ if $\itn e$ belongs to the empire of $\itn v$, and undefined otherwise.
\end{definition}

@@

\begin{lemma}
If the permutation $\links\sim\links'$ consists of the re-attachment of exactly one jump, then from $\coitn\links$ to $\coitn{\links'}$ at most one edge is taken from one appropriate vertex to another.
\end{lemma}

\begin{proof}[Proof sketch]
At most, a link can re-connect from vertex-gadget $v$ to vertex-gadget $w$, moving a number of chained edge-gadgets from $v$ to $w$.
%
But at most one edge is appropriate for both $v$ and $w$.
\end{proof}

\begin{lemma}
In a proof net for $\itn G$, for each vertex $v$, the weights of the appropriate edge-gadgets in the empire of $\itn v$ are equal to or greater than the constraint of $v$.
\end{lemma}

@@

\begin{definition}
The interpretation $\itn\gamma$ of a configuration $\gamma$ for a graph $G$ is the set of proof nets for $\itn G$ satisfying the following constraint: if $\gamma(e)=v$ then $\itn e$ belongs to the empire of $\itn v$
\end{definition}

>>>>

A \emph{configuration} of an \textsc{ncg} is a partial function $\gamma\colon E\rightharpoonup V$ such that
\begin{itemize}
	\item
for every edge $e$, if $\gamma(e)$ is defined then $\gamma(e)\in v(e)$, and
	\item
for every vertex $v$, the sum of its inflow weights is at least its inflow constraint, $\sum\{w(e)\mid \gamma(e)=v\}\geq c(v)$.
\end{itemize}

A \emph{reconfiguration step} $\gamma\sim\delta$ connects two configurations for an \textsc{ncg} $G$ that differ in the assignment $\gamma(e)$ of exactly one edge.

@@

@@

\begin{lemma}
\label{lem:appropriate edge weights}
In a proof net for $\itn G$, for each vertex $v$, the weights of the appropriate edge-gadgets in the empire of $\itn v$ are equal to or greater than the constraint of $v$.
\end{lemma}

@@

Then using the above, a proof net for $\itn G$ may be interpreted as a configuration for $G$.

\begin{definition}
	For a proof net $\links$ for the interpretation of a graph $\itn G$, let $\coitn\links$ be the configuration for $G$ where $\coitn\links(e)$ is $v$ if 1) $e$ is appropriate for $v$ and 2) $\itn e$ belongs to the empire of $\itn v$, and undefined otherwise.
\end{definition}

\begin{lemma}
If $\links\sim\links'$ are proof nets for $\itn G$ then $\coitn\links\sim\coitn{\links'}$.
\end{lemma}

\begin{proof}
A single permutation $\links\sim\links'$ on proof nets may move a number of edge-gadgets $\itn{e_1},\dotso,\itn{e_n}$ in three ways: 1) out of the empire of a vertex-gadget $\int v$, 2) into the empire of a vertex-gadget $\int w$, or 3) both.
%
Then in both $\coitn\links$ and $\coitn{\links'}$ the edges $e_1$ through $e_n$ are mobile, since by Lemma~\ref{lem:appropriate edge weights} the empires of the vertex-gadgets $\itn v$ (in cases 1 and 3) and $\itn w$ (in cases 2 and 3) contain appropriate edge-gadgets other than $\itn{e_1}$ through $\itn{e_n}$ of sufficient combined weight.
%
It follows that in the graph $G$ the edges $e_1$ through $e_n$ can be moved away from $v$ and/or onto $w$ one at a time.

\end{proof}

%
%
%
%\begin{definition}
%The interpretation $\itn\gamma$ of a configuration $\gamma$ for a graph $G$ is the set of proof nets for $\itn G$ satisfying the following constraint: if $\gamma(e)=v$ then $\itn e$ belongs to the empire of $\itn v$
%\end{definition}
